---
title: "Homework 1"
author: "Shaina Trevino & JP"
date: "January 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rio)
library(here)
```

## Creating new visualizations through joins

#### _An exploration of Kaggle's open university learning analytics dataset_

### Background

For this homework we will use data from the online data science platform [kaggle](https://www.kaggle.com/). Kaggle is an online data science platform that began as a competitive platform for predictive modeling problems. Private organizations would offer a prize, usually in the range of \$25K-$100K, for the individual or team that could provide the best predictive model for their problem. This is still a primary function of the website (see active competitions [here](https://www.kaggle.com/competitions>)), but the website has grown and is now also a place to share datasets, compete in open competitions (where you can see others code), and generally learn different facets and approaches to data science in an applied way.

#### Getting Started

You can download the data we’ll use for this homework either from kaggle (requires you create an account with [kaggle](https://www.kaggle.com/rocki37/open-university-learning-analytics-dataset)) or [directly from the organization](https://analyse.kmi.open.ac.uk/open_dataset). The latter link is worth examining to learn more about the data, regardless.

A total of seven datasets (tables) related to an online learning analytics project should be included with your download. A number of keys link the various sources of data. I recommend reading through the documentation provided by the organization to better understand these keys.

```{r import_data}
student <- import(here("data", "studentInfo.csv"),
                  setclass = "tbl_df")

assessment <- import(here("data", "studentAssessment.csv"),
                          setclass = "tbl_df")

as_d <- import(here("data", "assessments.csv"),
               setclass = "tbl_df")

```

```{r keys, include = FALSE}
student %>% count(id_student, code_presentation, code_module) %>% filter(n>1)

assessment %>% count(id_student, id_assessment) %>%  filter(n>1)

as_d %>% count(code_module, id_assessment) %>%  filter(n>1)

```

### Assignment

This primary components of this assignment are highly open-ended. These are to

1. Use at least 3 mutating joins


```{r mj_assessments, message = FALSE}
j_as_d <- right_join(assessment, as_d, by = "id_assessment") %>%
  group_by(id_student, id_assessment) %>% 
  arrange(id_student) 
```

```{r mj_studentinfo, message = FALSE}
key_comp <- right_join(j_as_d, student) %>% 
  arrange(id_student)
```

```{r fct_relevel, include = FALSE}
key_comp <- key_comp %>% 
  mutate(final_result = factor(final_result, levels = c("Fail", 
                                                        "Withdrawn", 
                                                        "Pass", 
                                                        "Distinction")))
```

```{r mj_av_score}
av_score <- key_comp %>% 
  group_by(id_student) %>% 
  summarize(av_score = mean(score)) %>% 
  arrange(desc(av_score))

full <- full_join(av_score, key_comp, by = "id_student")
```

2. Use at least 1 filtering join

```{r filtering join, message = FALSE, warning = FALSE}
fj_d <- key_comp %>% 
  group_by(id_student, id_assessment, code_module) %>% 
  summarize(avg_score = mean(score, na.rm = TRUE))

fj_d_low <- fj_d %>%
  ungroup() %>% 
  filter(avg_score < (mean(avg_score, na.rm = TRUE) - 2*sd(avg_score, na.rm = TRUE)))
fj_d_low

semi_fj_d <- semi_join(fj_d, fj_d_low)
semi_fj_d
```


```{r delete_duplicates, include = FALSE, eval = FALSE}
## This code was not used in final version of rmd, but may be helpful in the future. 
student1 <- student %>% 
  group_by(id_student) %>% 
  select(id_student, gender, highest_education, final_result) %>% 
  arrange(id_student)

rj <- right_join(student1, av_score) %>% arrange(id_student) 

rj1 <- distinct(rj, id_student, .keep_all = TRUE) %>% arrange(id_student)

#some ids are repeated beacuse people took the test twice (different years/different results)
```

3. Produce at least 3 data displays


```{r data displays, message = FALSE, warning = FALSE}
ggplot(full, aes(x = score)) +
  geom_histogram(color = "white",
                 aes(fill = gender),
                 position = "dodge",
                 bins = 20) +
  coord_flip()
  

full <- full %>%
  mutate(assessment_type = recode(assessment_type, 'CMA' = 'CMA',
                                  'Exam' = 'Exam',
                                  'TMA' = 'TMA')) %>% 
  na.omit()

full %>% 
  ggplot(aes(x = assessment_type, 
             y = score, color = assessment_type)) +
  geom_boxplot()

ggplot(full, aes(x = final_result, 
                 fill = region)) +
  geom_bar(color = "white", 
           position = "dodge") +
  coord_flip()
```

Following the completion of these requirements, please reproduce the following figure.

```{r mj_plotdata}
pd <- key_comp %>% filter(assessment_type == "TMA") %>% 
  group_by(gender, final_result, highest_education) %>% 
  summarize(av_score = mean(score, na.rm = TRUE)) %>% 
  mutate(highest_education = fct_reorder(highest_education, av_score))
```

```{r plot, fig.height = 12}
ggplot(pd, aes(x = fct_relevel(highest_education,"No Formal quals", 
                               "Lower Than A Level", 
                               "A Level or Equivalent", 
                               "HE Qualification",
                               "Post Graduate Qualification"), y = av_score)) +
  geom_col(aes(fill = gender), position = "dodge", alpha = .6) +
  scale_fill_manual(values = c("#00BFC4", "#F8766D")) +
  facet_wrap(~ final_result, ncol = 1, strip.position = "top") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Average TMA Scores",
       subtitle = "Results displayed by Education, Gender, and Final Results Designation",
       x = "Highest Education",
       y = "Average Score",
       caption = "Data from Kuzilek, Hlosta, & Zdrahal (2017). 
       https://analyse.kmi.open.ac.uk/open_dataset",
       fill = "Gender")

```

